First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-06-29 ms.tex
Fixed integration time for PAPER result.

Our best result is a limit on the cosmological power spectrum of $\Delta^2 \leq 2.7 \times 10^4$ 
mK$^2$ at $k=0.27$ h~Mpc$^{-1}$ and $z=7.1$. This is lower than the GMRT 40 hour
limit ($\Delta^2 \le 6.15 \times 10^4$ mK$^2$ at $z=8.6$; \citealt{Paciga:2013}), but 
signficantly higher than the latest PAPER result which 
integrated nearly 1,000 hours ($\Delta^2 \le 502$ mK$^2$ at $z=8.4$; \citealt{Ali:2015}).
Several EoR experiments are reaching sensitivity levels where very low systematics
become dominant. The PAPER team saw evidence that antenna cross-talk and foreground
leakage was limiting their result at several scales. The LOFAR team has seen excess noise
and diffuse foreground suppression due to calibration \citep{Patil:2016}. It is essential
for EoR experiments to understand and overcome these systematics in order to reach
a cosmological detection.

>>>>

Our best result is a limit on the cosmological power spectrum of $\Delta^2 \leq 2.7 \times 10^4$ 
mK$^2$ at $k=0.27$ h~Mpc$^{-1}$ and $z=7.1$. This is lower than the GMRT 40 hour
limit ($\Delta^2 \le 6.15 \times 10^4$ mK$^2$ at $z=8.6$; \citealt{Paciga:2013}), but 
signficantly higher than the latest PAPER result which 
integrated over 700 hours ($\Delta^2 \le 502$ mK$^2$ at $z=8.4$; \citealt{Ali:2015}).
Several EoR experiments are reaching sensitivity levels where very low systematics
become dominant. The PAPER team saw evidence that antenna cross-talk and foreground
leakage was limiting their result at several scales. The LOFAR team has seen excess noise
and diffuse foreground suppression due to calibration \citep{Patil:2016}. It is essential
for EoR experiments to understand and overcome these systematics in order to reach
a cosmological detection.
